Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-09-26 nips_2018.tex
funding acknowledgments

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture. Work funded by NSF GRFP (K.E.) and NSF Award 
\#1753684 (D.R.)

>>>>

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
\#1753684, and the MUSE program (Darpa grant FA8750-14-2-0242).
